---
title: "Lists - In Class Exercises"
author: "Billy Huynh"
date: "DATA2401 InClass Day 8"
output:nhtml_document

---

# Exercises: 

Make a list that contains the information on a single playing card. Suit, face, and value. 

```{r}
card <- list(
  suit = "Heart",
  face = "Ace",
  value = "11"
)

```


Make a second list where each element contains all the options for suit, face, and value, respectively. 

```{r}
all_options <- list(
  suits = c("Clover", "Heart", "Diamond", "Spade"),
  faces = c("Ace", "2", "3", "4", "5", "6", "7", "8", "9", "10", "Jack", "Queen", "King"),
  values = c(1:11)
)
typeof(all_options[[1]])
```


If `Newlist <- list(a=1:10, b="Good morning", c="Hi")`, write an R statement that will add 1 to each element of the first vector in Newlist.

```{r}
Newlist <- list(a=1:10, b="Good morning", c="Hi")
Newlist[[1]] + 1

```

If `b <- list(a=1:10, c="Hello", d="AA")`, write an R expression that will give all elements of the first vector of b, except the second, and write another that returns only elements of `a` that are greater than 7.

```{r}
b <- list(a=1:10, c="Hello", d="AA")
a_without_2nd <- b[[1]][-2]
a_without_2nd

a_greater_than_seven <- b[[1]][b[[1]] > 7]
a_greater_than_seven
```

Let `x <- list(a=5:10, c="Hello", d="AA")`, write an R statement to add a new item z = "NewItem" to the list x.

```{r}
x <- list(a=5:10, c="Hello", d="AA")
x$z <- "NewItem"
x
```
